---
title: "final_model_report"
output: html_document
params:
  model_name: model_name
  final_data: final_data
  bec: bec
  covars: covars
  extra_pts: extra_pts
  mtry: mtry
  min_n: min_n
  ntrees: ntrees
  downsample_ratio: downsample_ratio
  smote_ratio: smote_ratio
  out_dir: out_dir
  final_model: final_model
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=FALSE,
                      warning = FALSE, message = FALSE,
                      results = 'show',
                      eval = TRUE)  ## flag eval = false for quick text edits

```


```{r setup libs, echo = FALSE}

model_name <- params$model_name
final_data <- params$final_data
bec <- params$bec
covars <- params$covars
extra_pts <- params$extra_pts
mtry <- params$mtry
min_n <- params$min_n
ntrees <- params$ntrees
downsample_ratio <- params$downsample_ratio
smote_ratio <- params$smote_ratio
out_dir <- params$out_dir
final_model <- params$final_model

# ## testing lines
#final_data <- final_data
#final_model <- final_model
#out_bgc_dir = out_bgc_dir
#mbaldf <- mbaldf

```


```{r summary, echo = FALSE, include = TRUE}

#covs <- names(final_data)
#covs <- covs[-grep(covs, pattern = "mapunit1")]

```


This model uses the following parameters:

* **model name:** `r model_name`
* **bec unit:** `r bec`
* **mapunit:** 'mapunit1'
* **model covariates : ** `r covars`
* **extra_points:** `r extra_pts`
* **mtry:** `r mtry`
* **min_n:** `r min_n`
* **ntrees:** `r ntrees`
* **downsample_ratio:** `r downsample_ratio`
* **smote_ratio:** `r smote_ratio`
* **output directory:** `r out_dir`






## Response variable: 

The following training points and frequency of points were used in the model.

```{r summary1, echo = FALSE, include = TRUE}

trDat <- final_data

munits <- unique(trDat$mapunit1)
nf_mapunits <- grep(munits, pattern = "_\\d", value = TRUE, invert = TRUE)

# switch out the predicted Nf units for "nonfor" catergory.
trDatnf <- trDat |> 
    dplyr::mutate(mapunit1 = ifelse(mapunit1  %in% nf_mapunits, "nonfor", mapunit1 ))


# calculate summary of raw training data set
trDat_sum <- trDat |> 
  dplyr::group_by(mapunit1) |> 
  dplyr::summarise(freq = dplyr::n()) |> 
  dplyr::mutate(prop = round(freq/sum(freq),3))

ggplot2::ggplot(trDat, ggplot2::aes(mapunit1)) +
  ggplot2::geom_bar() + 
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90))

ggplot2::ggplot(trDatnf, ggplot2::aes(mapunit1)) +
  ggplot2::geom_bar() + 
  ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90))

```



## Model results summary

```{r, model results, echo = FALSE, eval = TRUE}
# variable importance plot 
final_fit  <- tune::extract_fit_parsnip(final_model)

xx <- final_fit |>    vip::vip(num_features = 50)
xx

```
