---
title: "model_report"
output: html_document
params:
  model_name: model_name
  bec: bec
  train_data: train_data
  fuzz_matrix: fuzz_matrix
  covars: covars
  use_neighbours: use_neighbours
  extra_pts: extra_pts
  mtry: mtry
  min_n: min_n
  ntrees: ntrees
  nf_f_filter: nf_f_filter
  smote_ratio: smote_ratio
  downsample_ratio: downsample_ratio
  ref_acc: ref_acc
  out_dir: out_dir

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=FALSE,
                      warning = FALSE, message = FALSE,
                      results = 'show',
                      eval = TRUE)  ## flag eval = false for quick text edits

```



```{r params, echo = FALSE}
model_name <- params$model_name
bec <- params$bec
train_data <- params$train_data
fuzz_matrix <- params$fuzz_matrix
covars <- params$covars
use_neighbours<- params$use_neighbours
extra_pts<- params$extra_pts
mtry <- params$mtry
min_n <- params$min_n
ntrees<- params$ntrees
nf_f_filter <- params$nf_f_filter
downsample_ratio<- params$downsample_ratio
smote_ratio<- params$smote_ratio
ref_acc<- params$ref_acc
out_dir<- params$out_dir

```


```{r summary, echo = FALSE, include = TRUE}
trDat <- train_data|>
  dplyr::filter(position == "Orig")

```

This model uses the following parameters:

* **model name:** `r model_name`
* **bec unit:** `r bec`
* **mapunit:** 'mapunit1'
* **model covariates : ** `r covars`
* **use_neighbours:** `r use_neighbours`
* **extra_points:** `r extra_pts`
* **mtry:** `r mtry`
* **min_n:** `r min_n`
* **ntrees:** `r ntrees`
* **downsample_ratio:** `r downsample_ratio`
* **smote_ratio:** `r smote_ratio`
* **nf_f_filter:** `r nf_f_filter`
* **output directory:** `r out_dir`



## Response variable:

The following training points and frequency of points were used in the model
(note this graph includes all points (pure and alternate), only pure points used in the model build.


```{r summary1, echo = FALSE, include = TRUE}

  # calculate summary of raw training data set
  trDat_sum <- trDat|>
    dplyr::group_by(mapunit1)|>
    dplyr::summarise(freq = dplyr::n())|>
    dplyr::mutate(prop = round(freq/sum(freq),3))

  ggplot2::ggplot(trDat_sum , ggplot2::aes(mapunit1, freq)) +
    ggplot2::geom_bar(stat = "identity") +
    ggplot2::geom_text(ggplot2::aes(mapunit1, freq, label = freq), vjust=-0.25)+
    ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90)) 


  # calculate the values of

  munits <- unique(trDat$mapunit1)
  nf_mapunits <- grep(munits, pattern = "_\\d", value = TRUE, invert = TRUE)

  # switch out the predicted Nf units for "nonfor" catergory.
  trDatnf <- trDat|>
    dplyr::mutate(mapunit1 = ifelse(.data$mapunit1 %in% nf_mapunits, "nonfor", .data$mapunit1 ))

  # calculate summary of raw training data set
  trDat_sumnf <- trDatnf |>
    dplyr::group_by(mapunit1)|>
    dplyr::summarise(freq = dplyr::n())|>
    dplyr::mutate(prop = round(freq/sum(freq),3))

  ggplot2::ggplot(trDat_sumnf  , ggplot2::aes(mapunit1, freq)) +
    ggplot2::geom_bar(stat = "identity") +
    ggplot2::geom_text(ggplot2::aes(mapunit1, freq, label = freq), vjust=-0.25)+
    ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90))

  trDat_slices <- trDat|>
    dplyr::group_by (slice)|>
    dplyr::summarise(n.transect = length(unique(transect_id)),
                     n.sites = length(unique(tid)))|>
    tidyr::pivot_longer(cols = c("n.transect", "n.sites"), names_to = "type", values_to = "number")

  ggplot2::ggplot(trDat_slices, ggplot2::aes(slice, number, fill = type)) +
    ggplot2::geom_bar(stat = "identity", position = "dodge") 

```

## Comparison of leave-one-out model results

```{r, LOO overall accuracy with confidence intervals, echo = FALSE, eval = TRUE}
  #Compare the LOO metrics to test metrics to see model fit

  acc <- ref_acc|>
    dplyr::select(mapunit1, slice, acc, kap, oob, spat_p_theta_1 ,spat_p_theta_0, aspat_p_theta_1 ,aspat_p_theta_0 )|>
    dplyr::distinct()|>
    dplyr::mutate(slice = factor(slice)) |>
    dplyr::mutate(oob = 1-oob)

  acc2 <- acc |>
    tidyr::pivot_longer(cols = dplyr::where(is.numeric), names_to = "accuracy_type", values_to = "value")|>
    dplyr::distinct()|>
    dplyr::mutate(type = dplyr::case_when(
      accuracy_type %in% c("acc", "kap", "oob") ~ "0_machine",
      stringr::str_detect(accuracy_type, "^spat_p_theta") ~ "1_spatial",
      stringr::str_detect(accuracy_type, "aspat_p_theta") ~ "2_aspatial"))|>
    dplyr::filter(!is.na(type))|>
    dplyr::filter(!accuracy_type == "slice")|>
    dplyr::mutate(accuracy_type = stringr::str_replace(accuracy_type, "aspat_p_theta_", "\u0398 "),
                  accuracy_type = stringr::str_replace(accuracy_type, "^spat_p_theta_", "\u0398 "))|>
    dplyr::mutate(accuracy_type = factor(accuracy_type), type = factor(type))


  acc2 <- acc2|>
    dplyr::mutate(accuracy_type = stringr::str_replace(accuracy_type, "theta1", "theta 1"),
                  accuracy_type = stringr::str_replace(accuracy_type, "theta0", "theta 0"),
                  accuracy_type = stringr::str_replace(accuracy_type, "aspat_p_theta", "\u0398 "),
                  accuracy_type = stringr::str_replace(accuracy_type, "aspat_pa_theta", "\u0398 "),
                  accuracy_type = stringr::str_replace(accuracy_type, "spat_paf_theta", "\u0398 "),
                  accuracy_type = stringr::str_replace(accuracy_type, "spat_pa_theta", "\u0398 "),
                  accuracy_type = stringr::str_replace(accuracy_type, "spat_p_theta", "\u0398 "))


  overall_acc <- ggplot2::ggplot(ggplot2::aes(y = value, x = factor(accuracy_type, level = c("kap",  "acc", "oob", "Θ  1", "Θ .5", "Θ  0")), fill = slice), data = acc2 ) +
    ggplot2::geom_boxplot() +
    ggplot2::scale_fill_brewer(type = "qual") +
    ggplot2::facet_grid(~type, labeller = ggplot2::labeller(type =
                                                              c("0_machine" = "machine", "1_spatial" = "spatial",
                                                                "2_aspatial" = "aspatial")), scales = "free_x")+
    ggplot2::geom_hline(yintercept = 0.65,linetype ="dashed", color = "black") +
    ggplot2::scale_fill_manual(values=c("grey90", "grey75", "grey50", "grey35","grey10"))+
    ggplot2::theme(axis.text.x = ggplot2::element_text(angle = 90, hjust = 1), legend.position="none") +
    ggplot2::xlab("Metric") + ggplot2::ylab("Accuracy") +
    ggplot2::ylim(0, 1)

  overall_acc
```


```{r, cv vs test overall accuracy with confidence intervals, echo = FALSE, eval = TRUE}

  acc_sum <- ref_acc|>
    dplyr::select(slice, kap, acc, oob,
                  aspat_p_theta_0, aspat_p_theta_1,
                  aspat_pa_theta_0, aspat_pa_theta_1,
                   aspat_paf_theta_0, aspat_paf_theta_1,
                  spat_p_theta_0,  spat_p_theta_1,
                  spat_pa_theta_0,  spat_pa_theta_1,
                  spat_paf_theta_0,spat_paf_theta_1)|>
    dplyr::distinct() |>
    dplyr::mutate(oob = 1-oob)

  acc_sum_long <- acc_sum|>
    tidyr::pivot_longer(cols = dplyr::where(is.numeric), names_to = "accuracy_type", values_to = "value")|>
    dplyr::mutate(type = dplyr::case_when(
      stringr::str_detect(accuracy_type, "acc") ~ "machine",
      stringr::str_detect(accuracy_type, "kap") ~ "machine",
      stringr::str_detect(accuracy_type, "oob") ~ "machine",
      stringr::str_detect(accuracy_type, "aspat_") ~ "aspatial",
      stringr::str_detect(accuracy_type, "spat_") ~ "spatial"))|>
    dplyr::mutate(accuracy_type_label = dplyr::case_when(
      stringr::str_detect(accuracy_type, "acc") ~ "machine",
      stringr::str_detect(accuracy_type, "kap") ~ "machine",
      stringr::str_detect(accuracy_type, "oob") ~ "machine",
      stringr::str_detect(accuracy_type, "_p_") ~ "p",
      stringr::str_detect(accuracy_type, "_pa_") ~ "pa",
      stringr::str_detect(accuracy_type, "_paf_") ~ "paf")) |>
    dplyr::mutate(valuepc = value*100)

  acc_sum_long <- acc_sum_long|>
    dplyr::rowwise()|>
    dplyr::mutate(theta = ifelse(type != "machine", stringr::str_sub(accuracy_type , start = -1),NA))|>  #regmatches(acc_sum_long$accuracy_type,regexpr("[0-9]+",acc_sum_long$accuracy_type)), accuracy_type))|>
    dplyr::mutate(theta = dplyr::case_when(
      theta == 5 ~ '0.5',
      accuracy_type == "kap" ~ "kap",
      accuracy_type == "acc" ~ "acc",
      accuracy_type == "oob" ~ "1-oob",
      .default = theta))

  # # set up order for plots
  acc_sum_long$type_f = factor(acc_sum_long$accuracy_type_label, levels = c("p" ,"pa", "paf"))

  p2 <- ggplot2::ggplot(ggplot2::aes(y = valuepc, x = factor(theta, level = c('acc', "kap", "1-oob","1", "0.5", "0")), fill = type), data = acc_sum_long ) +
    ggplot2::geom_boxplot() +
    ggplot2::facet_wrap(~accuracy_type_label, scales = "free_x", nrow = 1) +
    ggplot2::geom_hline(yintercept = 65,linetype ="dashed", color = "black") +
    ggplot2::ggtitle("Accuracy measures (median + quartiles)") +
    ggplot2::xlab("Metric") + ggplot2::ylab("Accuracy") +
    ggplot2::ylim(-0.05, 100)

  p2

```

## Accuracy per mapunit

We can compare map unit accuracy levels to assess under or acceptable performance per map units.

```{r generate overall mapunit, echo = FALSE, eval = TRUE}

#acc_plot_mu(acc_output, type = "spat")

#
# mu_acc <- acc_output|> 
#   dplyr::select(mapunit1, spat_p, spat_pa, spat_paf)
#
# mu_long <- mu_acc|> 
#      tidyr::pivot_longer(cols = where(is.numeric), names_to = "accuracy_type", values_to = "value")|> 
#   mutate(accuracy_label = sub(".*_", "", accuracy_type))%>%
#   mutate(valuepc = value*100)
#
#
# p4 <- ggplot(aes(y = valuepc, x = mapunit1, fill = accuracy_type), data = mu_long ) +
#    geom_boxplot(aes(middle = mean(valuepc))) +
#    ggtitle("Mapunit accuracy measures ") +
#    xlab("accuracy measure") + ylab("Proportion of Accurate calls") +
#   # ylim(-0.05, 1)+
#    theme_pem_facet()+
#    scale_fill_discrete_sequential(palette = "Light Grays")+
#   theme(axis.text.x=element_text(angle = 90, vjust = 0.5))
#
# p4

